Community-Conditioned Language Models

### 2020-11-20 paper/paper.tex
2 paragraphs on related work

In this work, we present results using a conditioned neural language models
to model variation between speech communities.
The architecture of these models concatenates a vector representation
of the conditioned variable to the input of the sequence model.
This approach has been applied in various conditioned text generation domains such as 
image captioning \citep{Vinyals2015}, machine translation \citep{Kalchbrenner2013},
but it has not, to our knowledeg, been used extensively to study linguistic variation.
There are, however some related methods that have been used to study variation,
and related applications of conditional neural language models.

In the later category, conditoinal nerual language models have been used to study linguistic change.

\paragraph{Vector representations of online communities encode semantic relationships}
https://www.aclweb.org/anthology/W17-2904.pdf

\paragraph{Reddit Mining to Understand Gendered Movements}
http://ceur-ws.org/Vol-2578/DARLIAP3.pdf

@@

\paragraph{Topic modelling}
- Discovering Discrete Latent Topics with Neural Variational Inference https://arxiv.org/pdf/1706.00359.pdf
- JeyHan Lau's work

\paragraph{Pre-trained language models}
- Unsupervised Domain Clusters in Pretrained Language Models https://www.aclweb.org/anthology/2020.acl-main.692/

>>>>

In this work, we present results using a conditioned neural language models
to model variation between speech communities.
The architecture of these models concatenates a vector representation
of the conditioned variable to the input of the sequence model.
This approach has been applied in various conditioned text generation domains such as 
image captioning \citep{Vinyals2015}, machine translation \citep{Kalchbrenner2013},
but it has not, to our knowledge, been used extensively to study linguistic variation.
There are, however some related methods that have been used to study variation,
and related applications of conditional neural language models.

In the later category, conditional neural language models have been
used to study linguistic change.

@@

\cite{khan2020reddit}

\paragraph{Pre-trained language models}
- Unsupervised Domain Clusters in Pretrained Language Models https://www.aclweb.org/anthology/2020.acl-main.692/ % 404?

\paragraph{Topic modelling}
Modelling communities is not unlike the classic task of \emph{topic
  modelling}. In topic modelling, one most often want to
\emph{discover} topics. In constrast, we take as a given that a given
message belongs to a given community. However, deep-learning topic
modelling is often built around the idea of a conditioned language
model \citep{Lau2017a}, with a separate topic-discovery module.

% - Discovering Discrete Latent Topics with Neural Variational Inference https://arxiv.org/pdf/1706.00359.pdf

% \paragraph{Vector representations of online communities encode semantic relationships}
% https://www.aclweb.org/anthology/W17-2904.pdf
